### 2016-12-10 source/paper.tex
-- Adding grunt config file. -- Adding npm package file. -- Adding source file. -- Adding class file.

% Define what kind of document we're going to write.
\documentclass[letterpaper, 10 pt, conference]{latex/classes/ieeeconf}

% Needed if you want to use the \thanks command.
% It appears to be like a footnote.
\IEEEoverridecommandlockouts

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document
\overrideIEEEmargins

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed

\title{\LARGE \bf
Preparation of Papers for IEEE Sponsored Conferences \& Symposia*
}

%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
%         \thanks{*Use the $\backslash$thanks command to put information here}\\
%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
%         University of Twente\\
%         7500 AE Enschede, The Netherlands\\
%         {\tt\small h.kwakernaak@autsubmit.com}}
%         \hspace*{ 0.5 in}
%         \parbox{3 in}{ \centering Pradeep Misra**
%         \thanks{**The footnote marks may be inserted manually}\\
%        Department of Electrical Engineering \\
%         Wright State University\\
%         Dayton, OH 45435, USA\\
%         {\tt\small pmisra@cs.wright.edu}}
%}

\author{Huibert Kwakernaak$^{1}$ and Pradeep Misra$^{2}$% <-this % stops a space
\thanks{*This work was not supported by any organization}% <-this % stops a space
\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
        University of Twente, 7500 AE Enschede, The Netherlands
        {\tt\small h.kwakernaak at papercept.net}}%
\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
        Dayton, OH 45435, USA
        {\tt\small p.misra at ieee.org}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

This electronic document is a live template. The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

This template, modified in MS Word 2003 and saved as Word 97-2003 \& 6.0/95 Ð RTF for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers. All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings. Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example. Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided. The formatter will need to create these components, incorporating the applicable criteria that follow.

\section{PROCEDURE FOR PAPER SUBMISSION}

\subsection{Selecting a Template (Heading 2)}

First, confirm that you have the correct template for your paper size. This template has been tailored for output on the US-letter paper size. Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.

\subsection{Maintaining the Integrity of the Specifications}

The template is used to format your paper and style the text. All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them. You may note peculiarities. For example, the head margin in this template measures proportionately more than is customary. This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document. Please do not revise any of the current designations

\section{MATH}

Before you begin to format your paper, first write and save the content as a separate text file. Keep your text and graphic files separate until after the text has been formatted and styled. Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph. Do not add any kind of pagination anywhere in the paper. Do not number text heads-the template will do that for you.

Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:

\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract. Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined. Do not use abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}

\begin{itemize}

\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as 3.5-inch disk drive.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: Wb/m2 or webers per square meter, not webers/m2.  Spell out units when they appear in text: . . . a few henries, not . . . a few H.
\item Use a zero before decimal points: 0.25, not .25. Use cm3, not cc. (bullet list)

\end{itemize}

\subsection{Equations}

The equations are an exception to the prescribed specifications of this template. You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font). To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled. Number equations consecutively. Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop. To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents. Italicize Roman symbols for quantities and variables, but not Greek symbols. Use a long dash rather than a hyphen for a minus sign. Punctuate equations with commas or periods when they are part of a sentence, as in

$$
\alpha + \beta = \chi \eqno{(1)}
$$

Note that the equation is centered using a center tab stop. Be sure that the symbols in your equation have been defined before or immediately following the equation. Use (1), not Eq. (1) or equation (1), except at the beginning of a sentence: Equation (1) is . . .

\subsection{Some Common Mistakes}
\begin{itemize}

\item The word data is plural, not singular.
\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter o.
\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an inset, not an insert. The word alternatively is preferred to the word alternately (unless you really mean something that alternates).
\item Do not use the word essentially to mean approximately or effectively.
\item In your paper title, if the words that uses can accurately replace the word using, capitalize the u; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones affect and effect, complement and compliment, discreet and discrete, principal and principle.
\item Do not confuse imply and infer.
\item The prefix non is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the et in the Latin abbreviation et al..
\item The abbreviation i.e. means that is, and the abbreviation e.g. means for example.

\end{itemize}

\section{USING THE TEMPLATE}

Use this sample document as your LaTeX source file to create your document. Save this file as {\bf root.tex}. You have to make sure to use the cls file that came with this distribution. If you use a different style file, you cannot expect to get required margins. Note also that when you are creating your out PDF file, the source file is only part of the equation. {\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size. Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output. }

It is impossible to account for all possible situation, one would encounter using \TeX. If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.

\subsection{Headings, etc}

Text heads organize the topics on a relational, hierarchical basis. For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic. If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced. Styles named Heading 1, Heading 2, Heading 3, and Heading 4 are prescribed.

\subsection{Figures and Tables}

Positioning Figures and Tables: Place figures and tables at the top and bottom of columns. Avoid placing them in the middle of columns. Large figures and tables may span across both columns. Figure captions should be below the figures; table heads should appear above the tables. Insert figures and tables after they are cited in the text. Use the abbreviation Fig. 1, even at the beginning of a sentence.

\begin{table}[h]
\caption{An Example of a Table}
\label{table_example}
\begin{center}
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{center}
\end{table}

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader. As an example, write the quantity Magnetization, or Magnetization, M, not just M. If including units in the label, present them within parentheses. Do not label axes only with units. In the example, write Magnetization (A/m) or Magnetization {A[m(1)]}, not just A/m. Do not label axes with a ratio of quantities and units. For example, write Temperature (K), not Temperature/K.

\section{CONCLUSIONS}

A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A conclusion might elaborate on the importance of the work or suggest applications and extensions.

\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
                                  % on the last page of the document manually. It shortens
                                  % the textheight of the last page by a suitable amount.
                                  % This command does not take effect until the next page
                                  % so it should come on the page before the last. Make
                                  % sure that you do not shorten the textheight too much.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

Appendixes should appear before the acknowledgment.

\section*{ACKNOWLEDGMENT}

The preferred spelling of the word acknowledgment in America is without an e after the g. Avoid the stilted expression, One of us (R. B. G.) thanks . . .  Instead, try R. B. G. thanks. Put sponsor acknowledgments in the unnumbered footnote on the first page.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
\bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication), IEEE J. Quantum Electron., submitted for publication.
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style), IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740Ð741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, Infrared navigationÑPart I: An assessment of feasibility (Periodical style), IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, A clustering technique for digital communications channel equalization using radial basis function networks, IEEE Trans. Neural Networks, vol. 4, pp. 570Ð578, July 1993.
\bibitem{c12} R. W. Lucky, Automatic equalization for digital communication, Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, On the compatibility of adaptive controllers (Published Conference Proceedings style), in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8Ð16.
\bibitem{c14} G. R. Faulhaber, Design of service systems with priority reservation, in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
\bibitem{c15} W. D. Doyle, Magnetization reversal in films with biaxial anisotropy, in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, Radio noise currents n short sections on bundle conductors (Presented Conference Paper style), presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
\bibitem{c17} J. G. Kreifeldt, An analysis of surface-detected EMG as an amplitude-modulated noise, presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
\bibitem{c18} J. Williams, Narrow-band analyzer (Thesis or Dissertation style), Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
\bibitem{c19} N. Kawasaki, Parametric study of thermal and chemical nonequilibrium nozzle flow, M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, Nonlinear resonant circuit devices (Patent style), U.S. Patent 3 624 12, July 16, 1990.

\end{thebibliography}

\end{document}

### 2016-12-10 gruntfile.js

@@ -1,0 +1,75 @@
+
+////////////////////////////////////////////////////////////////////////////////
+//
+//  Copyright (c) 2016, Perry L Miller IV
+//  All rights reserved.
+//
+////////////////////////////////////////////////////////////////////////////////
+
+////////////////////////////////////////////////////////////////////////////////
+//
+//  Grunt configuration file.
+//
+////////////////////////////////////////////////////////////////////////////////
+
+/* eslint-env node */
+
+module.exports = function ( grunt )
+{
+  // Initialize all the scripts we can run.
+  var scripts = require ( "./package.json" ).scripts;
+  var commands = {};
+  for ( var key in scripts )
+  {
+    commands[key] = { cmd: "npm", args: [ "run", key ] };
+  }
+
+  // All configuration goes here
+  var config = {
+
+    // The arbitrary commands to run, defined above.
+    run: commands,
+
+    // Configure what files to watch, and what to do when they change.
+    watch: {
+
+      // The scripts are a combination of the files to watch and the
+      // comands to run when they change.
+      scripts: {
+
+        // The files to watch.
+        files: [
+
+          // Configuration files.
+          "gruntfile.js",
+          "package.json",
+
+          // Classes, templates, styles, etc.
+          "latex/**/*.cls",
+
+          // Source of the paper.
+          "source/**/*.tex"
+        ],
+
+        // Do these tasks when a file changes.
+        tasks: [
+          "run:clear",
+          "run:build"
+        ],
+
+        // Do not spawn a child process to run the tasks.
+        options: { spawn: false }
+      }
+    }
+  };
+
+  // All configuration goes here
+  grunt.initConfig ( config );
+
+  // Tell grunt we plan to use these plug-ins.
+  grunt.loadNpmTasks ( "grunt-run" );
+  grunt.loadNpmTasks ( "grunt-contrib-watch" );
+
+  // What grunt should do when we type "grunt" into the terminal.
+  grunt.registerTask ( "default", [ "run:build" ] );
+};

### 2016-12-11 source/paper.tex
-- Using article class with two columns. -- Including eps and jpeg files as figures.

@@
 % Define what kind of document we're going to write.
-\documentclass[letterpaper, 10 pt, conference]{latex/classes/ieeeconf}
+\documentclass[twocolumn]{article}
 
-% Needed if you want to use the \thanks command.
-% It appears to be like a footnote.
-\IEEEoverridecommandlockouts
+% For including images.
+\usepackage{graphics}
 
-% See the \addtolength command later in the file to balance the column lengths
-% on the last page of the document
-\overrideIEEEmargins
+% For including encapsulated postscript files.
+\usepackage{epsfig}
 
-% The following packages can be found on http:\\www.ctan.org
-%\usepackage{graphics} % for pdf, bitmapped graphics files
-%\usepackage{epsfig} % for postscript graphics files
-%\usepackage{mathptmx} % assumes new font selection scheme installed
-%\usepackage{times} % assumes new font selection scheme installed
-%\usepackage{amsmath} % assumes amsmath package installed
-%\usepackage{amssymb}  % assumes amsmath package installed
+% Needed to use the geometry command.
+\usepackage{geometry}
 
-\title{\LARGE \bf
-Preparation of Papers for IEEE Sponsored Conferences \& Symposia*
-}
+% Set the size of the paper and the margins.
+\geometry{letterpaper, portrait, margin=0.5in}
 
-%\author{ \parbox{3 in}{\centering Huibert Kwakernaak*
-%         \thanks{*Use the $\backslash$thanks command to put information here}\\
-%         Faculty of Electrical Engineering, Mathematics and Computer Science\\
-%         University of Twente\\
-%         7500 AE Enschede, The Netherlands\\
-%         {\tt\small h.kwakernaak@autsubmit.com}}
-%         \hspace*{ 0.5 in}
-%         \parbox{3 in}{ \centering Pradeep Misra**
-%         \thanks{**The footnote marks may be inserted manually}\\
-%        Department of Electrical Engineering \\
-%         Wright State University\\
-%         Dayton, OH 45435, USA\\
-%         {\tt\small pmisra@cs.wright.edu}}
-%}
+% Distance between columns.
+\setlength{\columnsep}{0.4in}
 
-\author{Huibert Kwakernaak$^{1}$ and Pradeep Misra$^{2}$% <-this % stops a space
-\thanks{*This work was not supported by any organization}% <-this % stops a space
-\thanks{$^{1}$H. Kwakernaak is with Faculty of Electrical Engineering, Mathematics and Computer Science,
-        University of Twente, 7500 AE Enschede, The Netherlands
-        {\tt\small h.kwakernaak at papercept.net}}%
-\thanks{$^{2}$P. Misra is with the Department of Electrical Engineering, Wright State University,
-        Dayton, OH 45435, USA
-        {\tt\small p.misra at ieee.org}}%
-}
+% Set the title.
+\title{\LARGE \bf Your Awesome Title Here}
 
+% Set the author.
+\author{Your Name Here}
+
+% Start of the document.
 \begin{document}
 
+% Make the title
 \maketitle
-\thispagestyle{empty}
-\pagestyle{empty}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Start of the abstract.
 \begin{abstract}
 
-This electronic document is a live template.
-The various components of your paper [title, text, heads, etc.] are already defined on the style sheet, as illustrated by the portions given in this document.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
+% End of the abstract.
 \end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{INTRODUCTION}
+% New section.
+\section{Introduction}
 
-This template, modified in MS Word 2003 and saved as Word 97-2003 \& 6.0/95 Ð RTF for the PC, provides authors with most of the formatting specifications needed for preparing electronic versions of their papers.
-All standard paper components have been specified for three reasons: (1) ease of use when formatting individual papers, (2) automatic compliance to electronic requirements that facilitate the concurrent or later production of electronic products, and (3) conformity of style throughout a conference proceedings.
-Margins, column widths, line spacing, and type styles are built-in; examples of the type styles are provided throughout this document and are identified in italic type, within parentheses, following the example.
-Some components, such as multi-leveled equations, graphics, and tables are not prescribed, although the various table text styles are provided.
-The formatter will need to create these components, incorporating the applicable criteria that follow.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
-\section{PROCEDURE FOR PAPER SUBMISSION}
+% New section.
+\section{Details}
 
-\subsection{Selecting a Template (Heading 2)}
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
-First, confirm that you have the correct template for your paper size.
-This template has been tailored for output on the US-letter paper size.
-Please do not use it for A4 paper since the margin requirements for A4 papers may be different from Letter paper size.
+% New sub-section.
+\subsection{Figures}
 
-\subsection{Maintaining the Integrity of the Specifications}
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
 
-The template is used to format your paper and style the text.
-All margins, column widths, line spaces, and text fonts are prescribed; please do not alter them.
-You may note peculiarities.
-For example, the head margin in this template measures proportionately more than is customary.
-This measurement and others are deliberate, using specifications that anticipate your paper as one part of the entire proceedings, and not as an independent document.
-Please do not revise any of the current designations
+% A figure.
+\begin{figure}[h]
+\centering
+\includegraphics{figures/shapes.eps}
+\caption{These are some shapes.}
+\label{fig:shapes}
+\end{figure}
 
-\section{MATH}
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
 
-Before you begin to format your paper, first write and save the content as a separate text file.
-Keep your text and graphic files separate until after the text has been formatted and styled.
-Do not use hard tabs, and limit use of hard returns to only one return at the end of a paragraph.
-Do not add any kind of pagination anywhere in the paper.
-Do not number text heads-the template will do that for you.
+% A figure.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{figures/mountains.jpg}
+\caption{Majestic mountains.}
+\label{fig:mountains}
+\end{figure}
 
-Finally, complete content and organizational editing before formatting. Please take note of the following items when proofreading spelling and grammar:
+% New sub-section.
+\subsection{Bullets}
 
-\subsection{Abbreviations and Acronyms} Define abbreviations and acronyms the first time they are used in the text, even after they have been defined in the abstract.
-Abbreviations such as IEEE, SI, MKS, CGS, sc, dc, and rms do not have to be defined.
-Do not use abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-
+% Start some bullets.
 \begin{itemize}
 
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as 3.5-inch disk drive.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: Wb/m2 or webers per square meter, not webers/m2.  Spell out units when they appear in text: . . . a few henries, not . . . a few H.
-\item Use a zero before decimal points: 0.25, not .25. Use cm3, not cc. (bullet list)
+\item All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
+\item All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+\item All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+\item All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+\item All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+% End the bullets.
 \end{itemize}
 
+% New sub-section.
 \subsection{Equations}
 
-The equations are an exception to the prescribed specifications of this template.
-You will need to determine whether or not your equation should be typed using either the Times New Roman or the Symbol font (please no other font).
-To create multileveled equations, it may be necessary to treat the equation as a graphic and insert it into the text after your paper is styled.
-Number equations consecutively.
-Equation numbers, within parentheses, are to position flush right, as in (1), using a right tab stop.
-To make your equations more compact, you may use the solidus ( / ), the exp function, or appropriate exponents.
-Italicize Roman symbols for quantities and variables, but not Greek symbols.
-Use a long dash rather than a hyphen for a minus sign.
-Punctuate equations with commas or periods when they are part of a sentence, as in
+All work and no play makes Jack a dull boy.
 
@@
 
-Note that the equation is centered using a center tab stop.
-Be sure that the symbols in your equation have been defined before or immediately following the equation.
-Use (1), not Eq.
-(1) or equation (1), except at the beginning of a sentence: Equation (1) is .
-.
-.
+% New sub-section.
+\subsection{Figures}
 
-\subsection{Some Common Mistakes}
-\begin{itemize}
-
-\item The word data is plural, not singular.
-\item The subscript for the permeability of vacuum ?0, and other common scientific constants, is zero with subscript formatting, not a lowercase letter o.
-\item In American English, commas, semi-/colons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an inset, not an insert. The word alternatively is preferred to the word alternately (unless you really mean something that alternates).
-\item Do not use the word essentially to mean approximately or effectively.
-\item In your paper title, if the words that uses can accurately replace the word using, capitalize the u; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones affect and effect, complement and compliment, discreet and discrete, principal and principle.
-\item Do not confuse imply and infer.
-\item The prefix non is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the et in the Latin abbreviation et al..
-\item The abbreviation i.e. means that is, and the abbreviation e.g. means for example.
-
-\end{itemize}
-
-\section{USING THE TEMPLATE}
-
-Use this sample document as your LaTeX source file to create your document.
-Save this file as {\bf root.tex}.
-You have to make sure to use the cls file that came with this distribution.
-If you use a different style file, you cannot expect to get required margins.
-Note also that when you are creating your out PDF file, the source file is only part of the equation.
-{\it Your \TeX\ $\rightarrow$ PDF filter determines the output file size.
-Even if you make all the specifications to output a letter file in the source - if you filter is set to produce A4, you will only get A4 output.
-}
-
-It is impossible to account for all possible situation, one would encounter using \TeX.
-If you are using multiple \TeX\ files you must make sure that the ``MAIN`` source file is called root.tex - this is particularly important if your conference is using PaperPlaza's built in \TeX\ to PDF conversion tool.
-
-\subsection{Headings, etc}
-
-Text heads organize the topics on a relational, hierarchical basis.
-For example, the paper title is the primary text head because all subsequent material relates and elaborates on this one topic.
-If there are two or more sub-topics, the next level head (uppercase Roman numerals) should be used and, conversely, if there are not at least two sub-topics, then no subheads should be introduced.
-Styles named Heading 1, Heading 2, Heading 3, and Heading 4 are prescribed.
-
-\subsection{Figures and Tables}
-
-Positioning Figures and Tables: Place figures and tables at the top and bottom of columns.
-Avoid placing them in the middle of columns.
-Large figures and tables may span across both columns.
-Figure captions should be below the figures; table heads should appear above the tables.
-Insert figures and tables after they are cited in the text.
-Use the abbreviation Fig.
-1, even at the beginning of a sentence.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
@@
 \end{table}
+
+% New sub-section.
+\subsection{Tables}
+
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
@@
 
-\section{CONCLUSIONS}
+\section{Conclusion}
 
-A conclusion section is not required.
-Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
-A conclusion might elaborate on the importance of the work or suggest applications and extensions.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
-\addtolength{\textheight}{-12cm}   % This command serves to balance the column lengths
-                                  % on the last page of the document manually. It shortens
-                                  % the textheight of the last page by a suitable amount.
-                                  % This command does not take effect until the next page
-                                  % so it should come on the page before the last. Make
-                                  % sure that you do not shorten the textheight too much.
+\section*{Appendix}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgment}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{APPENDIX}
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
 
-Appendixes should appear before the acknowledgment.
-
-\section*{ACKNOWLEDGMENT}
-
-The preferred spelling of the word acknowledgment in America is without an e after the g.
-Avoid the stilted expression, One of us (R.
-B.
-G.) thanks .
-.
-.
-Instead, try R.
-B.
-G.
-thanks.
-Put sponsor acknowledgments in the unnumbered footnote on the first page.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-References are important to the reader; therefore, each citation must be complete and correct. If at all possible, references should be commonly available publications.
-
+% Start of the bibliography.
 \begin{thebibliography}{99}
@@
 \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
+
 \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
+
 \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
+
 \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
+
 \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
-\bibitem{c6} J. Wang, Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication), IEEE J. Quantum Electron., submitted for publication.
-\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
-\bibitem{c8} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style), IEEE Transl.
-J.
-Magn.Jpn., vol.
-2, Aug.
-1987, pp.
-740Ð741 [Dig.
-9th Annu.
-Conf.
-Magnetics Japan, 1982, p.
-301].
-\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
-\bibitem{c10} J. U. Duncombe, Infrared navigationÑPart I: An assessment of feasibility (Periodical style), IEEE Trans. Electron Devices, vol. ED-11, pp. 34Ð39, Jan. 1959.
-\bibitem{c11} S.
-Chen, B.
-Mulgrew, and P.
-M.
-Grant, A clustering technique for digital communications channel equalization using radial basis function networks, IEEE Trans.
-Neural Networks, vol.
-4, pp.
-570Ð578, July 1993.
-\bibitem{c12} R. W. Lucky, Automatic equalization for digital communication, Bell Syst. Tech. J., vol. 44, no. 4, pp. 547Ð588, Apr. 1965.
-\bibitem{c13} S.
-P.
-Bingulac, On the compatibility of adaptive controllers (Published Conference Proceedings style), in Proc.
-4th Annu.
-Allerton Conf.
-Circuits and Systems Theory, New York, 1994, pp.
-8Ð16.
-\bibitem{c14} G. R. Faulhaber, Design of service systems with priority reservation, in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3Ð8.
-\bibitem{c15} W. D. Doyle, Magnetization reversal in films with biaxial anisotropy, in 1987 Proc. INTERMAG Conf., pp. 2.2-1Ð2.2-6.
-\bibitem{c16} G.
-W.
-Juette and L.
-E.
-Zeffanella, Radio noise currents n short sections on bundle conductors (Presented Conference Paper style), presented at the IEEE Summer power Meeting, Dallas, TX, June 22Ð27, 1990, Paper 90 SM 690-0 PWRS.
-\bibitem{c17} J. G. Kreifeldt, An analysis of surface-detected EMG as an amplitude-modulated noise, presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
-\bibitem{c18} J. Williams, Narrow-band analyzer (Thesis or Dissertation style), Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
-\bibitem{c19} N. Kawasaki, Parametric study of thermal and chemical nonequilibrium nozzle flow, M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
-\bibitem{c20} J. P. Wilkinson, Nonlinear resonant circuit devices (Patent style), U.S. Patent 3 624 12, July 16, 1990.
 
+% End of the bibliography.
 \end{thebibliography}
 
+% End of the document.
 \end{document}

### 2016-12-11 gruntfile.js

@@ -41,6 +41,7 @@ module.exports = function ( grunt )
         files: [
 
           // Configuration files.
+          "ReadMe.md",
           "gruntfile.js",
           "package.json",
 

### 2016-12-11 paper.tex
Generating bibliography from citations used in paper

--- 2016-12-11 source/paper.tex
@@
 
+% The package for the bibliography.
+\usepackage{biblatex}
+
+% The name of the bibliography file.
+\addbibresource{source/references.bib}
+
 % Set the title.
-\title{\LARGE \bf Your Awesome Title Here}
+\title{\LARGE \bf My Paper Title}
 
@@
 
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
 % End of the abstract.
@@
 \section{Introduction}
+\label{sec:introduction}
 
 All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+\cite{knuthwebsite}
+All work and no play makes Jack a dull boy.
+
 All work and no play makes Jack a dull boy.
@@
 \section{Details}
+\label{sec:details}
 
 All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
 All work and no play makes Jack a dull boy.
@@
 \subsection{Figures}
+\label{sec:details_figures}
 
@@
 
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
 % A figure.
@@
 \centering
-\includegraphics[width=\linewidth]{figures/mountains.jpg}
+\includegraphics[width=\linewidth,natwidth=400,natheight=300]{figures/mountains.jpg}
 \caption{Majestic mountains.}
@@
 \subsection{Bullets}
+\label{sec:details_bullets}
 
@@
 \begin{itemize}
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
 
@@
 \subsection{Equations}
+\label{sec:details_equations}
 
@@
 % New sub-section.
-\subsection{Figures}
+\subsection{Tables}
+\label{sec:details_tables}
 
 All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
 All work and no play makes Jack a dull boy.
@@
 \caption{An Example of a Table}
-\label{table_example}
+\label{tab:table_a}
 \begin{center}
-\begin{tabular}{|c||c|}
+\begin{tabular}{|c||c|c|}
 \hline
-One & Two\\
+One & Two & Three\\
 \hline
-Three & Four\\
+Four & Five & Six\\
 \hline
@@
 
-% New sub-section.
-\subsection{Tables}
+\section{Conclusion}
+\label{sec:conclusions}
 
@@
 All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\begin{figure}[thpb]
-\centering
-\framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
-}}
-%\includegraphics[scale=1.0]{figurefile}
-\caption{Inductance of oscillation winding on amorphous
-magnetic core versus DC bias magnetic field}
-\label{figurelabel}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels.
-Use words rather than symbols or abbreviations when writing Figure axis labels to avoid confusing the reader.
-As an example, write the quantity Magnetization, or Magnetization, M, not just M.
-If including units in the label, present them within parentheses.
-Do not label axes only with units.
-In the example, write Magnetization (A/m) or Magnetization {A[m(1)]}, not just A/m.
-Do not label axes with a ratio of quantities and units.
-For example, write Temperature (K), not Temperature/K.
-
-\section{Conclusion}
 
@@
 All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+% New sub-section.
+\subsection{Important Stuff}
+\label{sec:conclusions_important_stuff}
+
 All work and no play makes Jack a dull boy.
@@
 \section*{Appendix}
+\label{sec:appendix}
 
-All work and no play makes Jack a dull boy.
 All work and no play makes Jack a dull boy.
@@
 \section*{Acknowledgment}
+\label{sec:acknowledgment}
 
@@
 
-% Start of the bibliography.
-\begin{thebibliography}{99}
+% Generate the bibliography.
+\printbibliography
 
-\bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
+% % Start of the bibliography.
+% \begin{thebibliography}{99}
 
-\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
+% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
 
-\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
+% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
 
-\bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
+% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
 
-\bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
+% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
 
-% End of the bibliography.
-\end{thebibliography}
+% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
+
+% % End of the bibliography.
+% \end{thebibliography}
 

### 2016-12-11 gruntfile.js

@@ -49,7 +49,8 @@ module.exports = function ( grunt )
           "latex/**/*.cls",
 
           // Source of the paper.
-          "source/**/*.tex"
+          "source/**/*.tex",
+          "source/**/*.bib"
         ],
 
         // Do these tasks when a file changes.

### 2016-12-11 source/paper.tex
Experimenting with directory structure

@@
 
+% The package for the bibliography.
+\usepackage{biblatex}
+
+% The name of the bibliography file.
+\addbibresource{references.bib}
+
 % Set the title.
-\title{\LARGE \bf Your Awesome Title Here}
+\title{\LARGE \bf My Paper Title}
 
@@
 \centering
-\includegraphics{figures/shapes.eps}
+\includegraphics{../figures/shapes.eps}
 \caption{These are some shapes.}
@@
 \centering
-\includegraphics[width=\linewidth]{figures/mountains.jpg}
+\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
 \caption{Majestic mountains.}

### 2016-12-11 gruntfile.js
Cleans temporary files before and after building

@@ -56,7 +56,9 @@ module.exports = function ( grunt )
         // Do these tasks when a file changes.
         tasks: [
           "run:clear",
-          "run:build"
+          "run:clean",
+          "run:build",
+          "run:clean"
         ],
 
         // Do not spawn a child process to run the tasks.

### 2016-12-11 source/conclusion.tex
-- Refactored into separate files. -- Added another reference.

--- 2016-12-11 paper.tex
@@
-% Define what kind of document we're going to write.
-\documentclass[twocolumn]{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Copyright (c) 2016, Perry L Miller IV
+%  All rights reserved.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% For including images.
-\usepackage{graphics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Conclusion file.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% For including encapsulated postscript files.
-\usepackage{epsfig}
-
-% Needed to use the geometry command.
-\usepackage{geometry}
-
-% Set the size of the paper and the margins.
-\geometry{letterpaper, portrait, margin=0.5in}
-
-% Distance between columns.
-\setlength{\columnsep}{0.4in}
-
-% The package for the bibliography.
-\usepackage{biblatex}
-
-% The name of the bibliography file.
-\addbibresource{source/references.bib}
-
-% Set the title.
-\title{\LARGE \bf My Paper Title}
-
-% Set the author.
-\author{Your Name Here}
-
-% Start of the document.
-\begin{document}
-
-% Make the title
-\maketitle
-
-% Start of the abstract.
-\begin{abstract}
+\section{Conclusion}
+\label{sec:conclusion}
 
 All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End of the abstract.
-\end{abstract}
-
-% New section.
-\section{Introduction}
-\label{sec:introduction}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-\cite{knuthwebsite}
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New section.
-\section{Details}
-\label{sec:details}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Figures}
-\label{sec:details_figures}
-
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-
-% A figure.
-\begin{figure}[h]
-\centering
-\includegraphics{figures/shapes.eps}
-\caption{These are some shapes.}
-\label{fig:shapes}
-\end{figure}
-
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% A figure.
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth,natwidth=400,natheight=300]{figures/mountains.jpg}
-\caption{Majestic mountains.}
-\label{fig:mountains}
-\end{figure}
-
-% New sub-section.
-\subsection{Bullets}
-\label{sec:details_bullets}
-
-% Start some bullets.
-\begin{itemize}
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End the bullets.
-\end{itemize}
-
-% New sub-section.
-\subsection{Equations}
-\label{sec:details_equations}
-
-All work and no play makes Jack a dull boy.
-
-$$
-\alpha + \beta = \chi \eqno{(1)}
-$$
-
-% New sub-section.
-\subsection{Tables}
-\label{sec:details_tables}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{tab:table_a}
-\begin{center}
-\begin{tabular}{|c||c|c|}
-\hline
-One & Two & Three\\
-\hline
-Four & Five & Six\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy \cite{knuthwebsite}.
 All work and no play makes Jack a dull boy.
@@
 % New sub-section.
-\subsection{Important Stuff}
+\subsection{Really Important Stuff}
 \label{sec:conclusions_important_stuff}
@@
 All work and no play makes Jack a dull boy.
-
-\section*{Appendix}
-\label{sec:appendix}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\section*{Acknowledgment}
-\label{sec:acknowledgment}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% Generate the bibliography.
-\printbibliography
-
-% % Start of the bibliography.
-% \begin{thebibliography}{99}
-
-% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
-
-% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-
-% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-
-% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
-
-% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
-
-% % End of the bibliography.
-% \end{thebibliography}
-
-% End of the document.
-\end{document}

### 2016-12-11 source/conclusion.tex
More references and another table
Referencing sections, tables, and figures
Using global variables
Sorting citations

@@
 All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy \cite{knuthwebsite}.
+All work and no play makes Jack a dull boy \cite{knuth-website}.
 All work and no play makes Jack a dull boy.
 All work and no play makes Jack a dull boy.
+
+As noted in sections
+\ref{sec:discussion_figures} and
+\ref{sec:discussion_equations}
+we have all work and no play making Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+\subsection{Important Stuff}
+\label{sec:conclusions_important_stuff}
+
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy
+\cite{einstein-electrodynamics,
+knuth-website,
+knuth-fundamental-algorithms,
+dirac-quantum-mechanics}.
+All work and no play makes Jack a dull boy.
+All work and no play makes Jack a dull boy.
+
+\subsection{Really Important Stuff}
+\label{sec:conclusions_really_important_stuff}
 
@@
 All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Really Important Stuff}
-\label{sec:conclusions_important_stuff}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.

### 2016-12-11 source/paper.tex
-- Refactored into separate files. -- Added another reference.
Using global variables
No page number on the first page
Sorting citations

@@
-% Define what kind of document we're going to write.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Copyright (c) 2016, Perry L Miller IV
+%  All rights reserved.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Main file.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Define what kind of document this is.
 \documentclass[twocolumn]{article}
 
-% For including images.
+% For including images and eps files.
 \usepackage{graphics}
-
-% For including encapsulated postscript files.
 \usepackage{epsfig}
 
-% Needed to use the geometry command.
+% Set the size of the paper, margins, etc.
 \usepackage{geometry}
-
-% Set the size of the paper and the margins.
 \geometry{letterpaper, portrait, margin=0.5in}
-
-% Distance between columns.
 \setlength{\columnsep}{0.4in}
 
-% The package for the bibliography.
-\usepackage{biblatex}
-
-% The name of the bibliography file.
+% Automatically generate the bibliography.
+\usepackage[
+  sortcites = true,        % \cite{a,d,b} --> [a,b,d]
+  citestyle = numeric-comp % \cite{a,c,b} --> [a-c]
+]{biblatex}
 \addbibresource{references.bib}
 
-% Set the title.
+% Set the title and author.
 \title{\LARGE \bf My Paper Title}
-
-% Set the author.
-\author{Your Name Here}
+\author{My Name}
 
@@
 
+% Define some variables used throughout.
+\include{definitions}
+
 % Make the title
@@
 
-% Start of the abstract.
-\begin{abstract}
+% No page number on the very first page.
+\thispagestyle{empty}
 
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End of the abstract.
-\end{abstract}
-
-% New section.
-\section{Introduction}
-\label{sec:introduction}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-\cite{knuthwebsite}
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New section.
-\section{Details}
-\label{sec:details}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Figures}
-\label{sec:details_figures}
-
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-
-% A figure.
-\begin{figure}[h]
-\centering
-\includegraphics{../figures/shapes.eps}
-\caption{These are some shapes.}
-\label{fig:shapes}
-\end{figure}
-
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% A figure.
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
-\caption{Majestic mountains.}
-\label{fig:mountains}
-\end{figure}
-
-% New sub-section.
-\subsection{Bullets}
-\label{sec:details_bullets}
-
-% Start some bullets.
-\begin{itemize}
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End the bullets.
-\end{itemize}
-
-% New sub-section.
-\subsection{Equations}
-\label{sec:details_equations}
-
-All work and no play makes Jack a dull boy.
-
-$$
-\alpha + \beta = \chi \eqno{(1)}
-$$
-
-% New sub-section.
-\subsection{Tables}
-\label{sec:details_tables}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{tab:table_a}
-\begin{center}
-\begin{tabular}{|c||c|c|}
-\hline
-One & Two & Three\\
-\hline
-Four & Five & Six\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Important Stuff}
-\label{sec:conclusions_important_stuff}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\section*{Appendix}
-\label{sec:appendix}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\section*{Acknowledgment}
-\label{sec:acknowledgment}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
+% Include the content.
+\input{abstract}
+\input{introduction}
+\input{discussion}
+\input{conclusion}
+\input{appendix}
+\input{acknowledgments}
 
@@
 
-% % Start of the bibliography.
-% \begin{thebibliography}{99}
-
-% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
-
-% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-
-% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-
-% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
-
-% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
-
-% % End of the bibliography.
-% \end{thebibliography}
-
 % End of the document.

### 2016-12-11 source/discussion/figures.tex
-- Refactored into separate files. -- Added another reference.
Referencing sections, tables, and figures
Added another image as a figure

--- 2016-12-11 source/paper.tex
@@
-% Define what kind of document we're going to write.
-\documentclass[twocolumn]{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Copyright (c) 2016, Perry L Miller IV
+%  All rights reserved.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% For including images.
-\usepackage{graphics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Discussion about figures.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% For including encapsulated postscript files.
-\usepackage{epsfig}
-
-% Needed to use the geometry command.
-\usepackage{geometry}
-
-% Set the size of the paper and the margins.
-\geometry{letterpaper, portrait, margin=0.5in}
-
-% Distance between columns.
-\setlength{\columnsep}{0.4in}
-
-% The package for the bibliography.
-\usepackage{biblatex}
-
-% The name of the bibliography file.
-\addbibresource{references.bib}
-
-% Set the title.
-\title{\LARGE \bf My Paper Title}
-
-% Set the author.
-\author{Your Name Here}
-
-% Start of the document.
-\begin{document}
-
-% Make the title
-\maketitle
-
-% Start of the abstract.
-\begin{abstract}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End of the abstract.
-\end{abstract}
-
-% New section.
-\section{Introduction}
-\label{sec:introduction}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-\cite{knuthwebsite}
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New section.
-\section{Details}
-\label{sec:details}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
 \subsection{Figures}
-\label{sec:details_figures}
+\label{sec:discussion_figures}
 
 Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
+See figures
+\ref{fig:shapes},
+\ref{fig:mountains}, and
+\ref{fig:lake} for details.
 Good, then we will shall fight in the shade.
@@
 \includegraphics{../figures/shapes.eps}
-\caption{These are some shapes.}
+\caption{Made with LibreOffice and saved as EPS.}
 \label{fig:shapes}
@@
 \includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
-\caption{Majestic mountains.}
+\caption{Misty Mountains from Unsplash It \cite{unsplash}.}
 \label{fig:mountains}
@@
 
-% New sub-section.
-\subsection{Bullets}
-\label{sec:details_bullets}
-
-% Start some bullets.
-\begin{itemize}
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End the bullets.
-\end{itemize}
-
-% New sub-section.
-\subsection{Equations}
-\label{sec:details_equations}
-
-All work and no play makes Jack a dull boy.
-
-$$
-\alpha + \beta = \chi \eqno{(1)}
-$$
-
-% New sub-section.
-\subsection{Tables}
-\label{sec:details_tables}
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
 
@@
 
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{tab:table_a}
-\begin{center}
-\begin{tabular}{|c||c|c|}
-\hline
-One & Two & Three\\
-\hline
-Four & Five & Six\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Important Stuff}
-\label{sec:conclusions_important_stuff}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\section*{Appendix}
-\label{sec:appendix}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\section*{Acknowledgment}
-\label{sec:acknowledgment}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% Generate the bibliography.
-\printbibliography
-
-% % Start of the bibliography.
-% \begin{thebibliography}{99}
-
-% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
-
-% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-
-% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-
-% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
-
-% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
-
-% % End of the bibliography.
-% \end{thebibliography}
-
-% End of the document.
-\end{document}
+% A figure.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/lake.jpg}
+\caption{A Mountain Lake from Unsplash It \cite{unsplash}.}
+\label{fig:lake}
+\end{figure}

### 2016-12-11 source/appendix.tex
-- Refactored into separate files. -- Added another reference.
Added a rotated image and one that spans both columns

--- 2016-12-11 paper.tex
@@
-% Define what kind of document we're going to write.
-\documentclass[twocolumn]{article}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Copyright (c) 2016, Perry L Miller IV
+%  All rights reserved.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% For including images.
-\usepackage{graphics}
-
-% For including encapsulated postscript files.
-\usepackage{epsfig}
-
-% Needed to use the geometry command.
-\usepackage{geometry}
-
-% Set the size of the paper and the margins.
-\geometry{letterpaper, portrait, margin=0.5in}
-
-% Distance between columns.
-\setlength{\columnsep}{0.4in}
-
-% The package for the bibliography.
-\usepackage{biblatex}
-
-% The name of the bibliography file.
-\addbibresource{source/references.bib}
-
-% Set the title.
-\title{\LARGE \bf My Paper Title}
-
-% Set the author.
-\author{Your Name Here}
-
-% Start of the document.
-\begin{document}
-
-% Make the title
-\maketitle
-
-% Start of the abstract.
-\begin{abstract}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End of the abstract.
-\end{abstract}
-
-% New section.
-\section{Introduction}
-\label{sec:introduction}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-\cite{knuthwebsite}
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New section.
-\section{Details}
-\label{sec:details}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Figures}
-\label{sec:details_figures}
-
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-
-% A figure.
-\begin{figure}[h]
-\centering
-\includegraphics{figures/shapes.eps}
-\caption{These are some shapes.}
-\label{fig:shapes}
-\end{figure}
-
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-Good, then we will shall fight in the shade.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% A figure.
-\begin{figure}[h]
-\centering
-\includegraphics[width=\linewidth,natwidth=400,natheight=300]{figures/mountains.jpg}
-\caption{Majestic mountains.}
-\label{fig:mountains}
-\end{figure}
-
-% New sub-section.
-\subsection{Bullets}
-\label{sec:details_bullets}
-
-% Start some bullets.
-\begin{itemize}
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\item All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% End the bullets.
-\end{itemize}
-
-% New sub-section.
-\subsection{Equations}
-\label{sec:details_equations}
-
-All work and no play makes Jack a dull boy.
-
-$$
-\alpha + \beta = \chi \eqno{(1)}
-$$
-
-% New sub-section.
-\subsection{Tables}
-\label{sec:details_tables}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-\begin{table}[h]
-\caption{An Example of a Table}
-\label{tab:table_a}
-\begin{center}
-\begin{tabular}{|c||c|c|}
-\hline
-One & Two & Three\\
-\hline
-Four & Five & Six\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\section{Conclusion}
-\label{sec:conclusions}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% New sub-section.
-\subsection{Important Stuff}
-\label{sec:conclusions_important_stuff}
-
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%  Appendix file.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section*{Acknowledgment}
-\label{sec:acknowledgment}
+% A figure using a JPG raster image file.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/lake.jpg}
+\caption{A Mountain Lake from Unsplash It \cite{unsplash}.}
+\label{fig:lake}
+\end{figure}
 
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-All work and no play makes Jack a dull boy.
-
-% Generate the bibliography.
-\printbibliography
-
-% % Start of the bibliography.
-% \begin{thebibliography}{99}
-
-% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
-
-% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
-
-% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
-
-% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.
-
-% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.
-
-% % End of the bibliography.
-% \end{thebibliography}
-
-% End of the document.
-\end{document}
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.
+Good, then we will shall fight in the shade.

### 2016-12-11 source/discussion/figures.tex
Added a rotated image and one that spans both columns

@@
 
-% A figure.
+% A figure using an EPS vector image file.
 \begin{figure}[h]
@@
 
-% A figure.
+% A figure using a JPG raster image file.
 \begin{figure}[h]
@@
 All work and no play makes Jack a dull boy.
+Figure \ref{fig:outdoor_cafe} demonstrates how we can make an image span both columns.
 
-% A figure.
-\begin{figure}[h]
+% A figure that spans both columns.
+\begin{figure*}[h]
 \centering
-\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/lake.jpg}
-\caption{A Mountain Lake from Unsplash It \cite{unsplash}.}
-\label{fig:lake}
-\end{figure}
+\includegraphics[width=\textwidth,natwidth=800,natheight=600]{../figures/outdoor_cafe.jpg}
+\caption{Outdoor Cafe from Unsplash It \cite{unsplash}.}
+\label{fig:outdoor_cafe}
+\end{figure*}
